\documentclass{resume} % Use the custom resume.cls style

% pacakages
\usepackage{fontawesome}
\usepackage{fancybox}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Galymzhan Turysbekov} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+7 (771) 624-45-47, Kazakhstan} 
\address{\href{mailto:galymzhan.turysbekov@nu.edu.kz}{Email: galymzhan.turysbekov@nu.edu.kz} \hspace{0.4cm} \href{https://www.linkedin.com/in/galymzhan-turysbekov/}{LinkedIn: galymzhan-turysbekov} \hspace{0.4cm} \href{https://gitlab.com/gturysbekov}{GitLab: @gturysbekov}}  %

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\href{https://nu.edu.kz/}{\textcolor{black}{{\bf \textbf{Nazarbayev University}}}}, \textit {Bachelor of Computer Science} \href{https://nu.edu.kz/}{\textcolor{black}{{\small \faExternalLink}}} \hfill \textit {Sep. 2021 - June 2025 (expected)}
\begin{itemize}
     \item \textbf{Relevant Coursework:} Algorithms, Performance and Data Structures, Discrete Mathematics, Linear Algebra.
 \end{itemize}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

 % ------
 
% \begin{rSection}{EXPERIENCE}

% \textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
% Company Name \hfill \textit{San Francisco, CA}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved X\% growth for XYZ using A, B, and C skills.
%      \item Led XYZ which led to X\% of improvement in ABC
%     \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}
 
% \textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
% Company Name \hfill \textit{San Francisco, CA}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved X\% growth for XYZ using A, B, and C skills.
%      \item Led XYZ which led to X\% of improvement in ABC
%     \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}

% \end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}

\item \href{https://gitlab.com/gturysbekov/football-players/-/tree/master?ref_type=heads}{\textcolor{blue}{\textbf{Football Players Database.}} {\textcolor{black}{\small \faExternalLink}}}
\vspace{-5pt} \item \ovalbox {Java} \hspace{0cm} \ovalbox {Hibernate} \hspace{0cm} \ovalbox {Spring} \hspace{0cm} \ovalbox {PostgreSQL}
\begin{itemize}
    \itemsep -5pt 
     \item Built a database on \underline {\textbf{Java}} that stores football players. 
     \item Used \underline{\textbf{Spring Security}}, and \underline{\textbf{JWT}} Tokens to implement basic registration and authorization for users. Also added dependencies to methods based on roles that are attached to users.
 \end{itemize}

 \item \href{https://gitlab.com/gturysbekov/minishop/-/tree/master?ref_type=heads}{\textcolor{blue}{\textbf{MiniShop}} {\textcolor{black}{\small \faExternalLink}}} 
\vspace{-5pt} \item \ovalbox {Java} \hspace{0cm} \ovalbox {Flyway} \hspace{0cm} \ovalbox {Spring}
\begin{itemize}
    \itemsep -5pt 
     \item Built a mini shop using \underline {\textbf{Spring}}, where you make order and get information about your purchases. 
     \item Implemented basic authorization and security. Moreover, specified the transactions on several methods.
 \end{itemize}

\item \href{https://gitlab.com/gturysbekov/game_2048/-/tree/master?ref_type=heads}{\textcolor{blue}{\textbf{2048 Game}} {\textcolor{black}{\small \faExternalLink}}} 
\vspace{-5pt} \item \ovalbox {Java} \hspace{0cm} \ovalbox {OOP} \hspace{0cm} \ovalbox {GUI}
\begin{itemize}
    \itemsep -5pt 
     \item Built the '2048' game on \underline {\textbf{Java}} using \underline{\textbf{OOP}} principles, which is based on connecting tiles.
     \item Used \underline {\textbf{GUI}} to create interface visible to user, and also made it possible to keep the best score.
     \item Implemented 4 levels for the game (easy, medium, hard, auto-play). 
 \end{itemize}
 
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 

\href{https://astanahub.com/en/l/TechOrdaStudents}{\textbf{\large \textcolor{black}{Sapsan Code, Backend Development {\small \faExternalLink} } } }  \hfill \textit {Nov. 2022 - May 2023 (expected)} 
\vspace{-4pt}
\begin{itemize}
    \itemsep -5pt 
     \item Awarded 600.000-tenge scholarship to study under the “Tech Orda” program.
     \item \textcolor{blue}{\textbf{Backend Development}}: completed 6-month course in programming school "Sapsan Code" (Java). 
     \item Deeply studied backend development on Java programming language by creating several projects.
 \end{itemize}

\textbf{\large "Dombyra" musical instrument Coach} \hfill \textit {March 2022 - May 2022}
\vspace{-4pt}
\begin{itemize}
    \itemsep -5pt
     \item \textcolor{blue}{\textbf{Headed a group of 20 students}} to playing the Kazakh musical instrument "Dombyra".
     \item Increased interest in playing the instrument among foreign students.
 \end{itemize}

\textbf{\large Table Tennis Coach} \hfill \textit {June 2022 - Nov. 2022}
\vspace{-4pt}
\begin{itemize}
    \itemsep -5pt
     \item Contributed to the development of the table tennis community at the university, by conducting table tennis training for local and international students.
      \item \textcolor{blue}{\textbf{Trained a group of 10 students}} on playing table tennis at university, 3 of which were included to the University team.
 \end{itemize}
 
\textbf{\large Volunteering Work}
\vspace{-4pt}
\begin{itemize}
    \itemsep -5pt 
     \item Actively participated in the volunteering activities of the university by helping in organization of various events. 
     \item Volunteered on the "2022 class Graduation Ceremony", "Charity trial run for Aizia", "XIII Charity Bazaar".
 \end{itemize}
 


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS AND INTERESTS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
\textbf{Programming Languages}: & Java, C++, Python (basic), C
\\
\textbf{Languages}: & Kazakh (native), Russian (native), English (fluent), Turkish (elementary)
\\
\textbf{Technologies}: & Spring, Git, PostgreSQL, Flyway, GUI\\
\end{tabular}\\
\end{rSection}



\end{document}
